### 2016-05-01 ch01-intro/introduction.tex
Ch01 finished?

\section{System Identification}

System identification is the science that deals with converting observations of a system into mathematical models to describe the behavior of the system under test.
Successfully identifying a system often hinges on a plethora of choices that are to be made by the user.
As a result, system identification can also be seen as an art for which the practitioner needs to learn the tricks of the trade.
In \figref{fig:intro:identification-cycle}, a high-level flow diagram containing some key steps that are performed when identifying a system.
For the technical details, we refer to the many textbooks on system identification~\citep{Soderstrom1989,Ljung1999,Pintelon2012}.
Here, we give the high-level overview of the different steps and choice.

@@

\subsection{System Identification Approaches}
In this section, some different approaches for system identification are discussed and related to the work in this dissertation.
We cover some typical traits of different methods and describe why a particular approach is favored in this thesis.

@@

\subsubsection{Parametric or non-parametric}

\subsubsection{Linear or nonlinear?}
\subsubsection{Time invariant or not?}

\subsubsection{Time or Frequency Domain}

>>>>

\section{System Identification}
System identification is the science that deals with converting observations of a system into mathematical models to describe the behavior of the system under test.
Successfully identifying a system often hinges on a plethora of choices that are to be made by the user.
As a result, system identification can also be seen as an art for which the practitioner needs to learn the tricks of the trade.
In \figref{fig:intro:identification-cycle}, a high-level flow diagram containing some key steps that are performed when identifying a system.
For the technical details, we refer to the many textbooks on system identification~\citep{Soderstrom1989,Ljung1999,Pintelon2012}.
Here, we give the high-level overview of the different steps.

@@

\subsection{System Identification Choices}
In this section, some different approaches for system identification are discussed and related to the work in this dissertation.
We cover some typical traits of different methods and describe why a particular approach is favored in this thesis.

@@

\subsubsection{Linear or nonlinear?}
A preliminary choice that is often made, is to first try linear models.
Linear models guarantee that superposition of input-signals results in the superposition of the corresponding output signals.
Specifically, if a linear system maps the output $u_i$ to the output signal $y_i$ (for any value of $i$), then an input $\sum_i u_i$ is mapped to the output $\sum_i y_i$.
As such, the output of a system is (linearly) proportional to its input.
This is a very powerful property that allows to simplify reasoning about such systems.
The implications of this powerful property can be verified textbooks covering signals and systems~\citep{Oppenheim1996,Mandal2007,Kailath1980}.
For non-linear systems, the superposition property is no longer guaranteed.

In practice, all systems behave in a nonlinear way to some degree.
Just imagine riding a bike: when you are cruising at a constant speed, pedaling at a faster pace will make the bike go proportionally faster.
However, once you come to a full stop at a traffic light and want to start riding again, you need to apply a disproportionate amount of force to put the bike to motion again (due to friction).

In this dissertation, we assume the system behaves in a dominantly linear way.
No specific care is taken of nonlinearities.
However, even with dominantly linear models~\citep{Schoukens2004}, nonlinear systems can often be well-described.
Nevertheless, building a model to characterize the nonlinearities in a structured way requires a lot more effort~\citep{Ljung2010,Giri2010,Sjoberg1995}.
However, e.g. for block-oriented nonlinear models~\citep{Giri2010}, some of the intermediate steps require identification of linear blocks.
